---
title: "Using the chemcalc package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the chemcalc package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Make sure the package is loaded before using the functions. 

```{r setup}
library(chemcalc)
```

## Molar Mass Calculation

The calculate_molar_mass() function allows you to compute the molar mass of a compound by parsing its chemical formula and summing the atomic masses of its constituent elements.

```{r}
calculate_molar_mass("H2O")
```
You can also use more complex formulas with multiple elements and counts:
```{r}
calculate_molar_mass("C6H12O6")  # Glucose
```
This is useful in stoichiometry problems where you need the molar mass to convert between grams and moles.

## Dilution Calculations (C1V1 = C2V2)

The dilution_c1v1() function calculates the missing value specified by user in the dilution equation (C1 * V1 = C2 * V2). Only one of the four parameters should be left NULL. For example, finding the dilution of C2 :

```{r}
dilution_c1v1(C1 = 2, V1 = 50, V2 = 100)  # Returns C2
```
To find the initial volume (V1) needed to prepare a diluted solution:
```{r}
dilution_c1v1(C1 = 5, C2 = 1, V2 = 100)
```

If more than one or none of the parameters are NULL, the function will stop with an error to guide proper usage.

## Percent Yield
The percent_yield() function calculates the efficiency of a reaction based on the actual and theoretical yields given.

```{r}
percent_yield(actual = 3.5, theoretical = 5)  # Should return 70
```
This is can be useful for lab-based evaluations of reaction success or determining optimization. 
